GSE158422: DNA methylation in Lung squamous cell carcinoma - gene methylation enrichment analysis - sensitivity analysis

### 2023-11-16 figs/GSE158422_sensitivity.Rmd
finish

suppressPackageStartupMessages({
  library("limma")
  library("eulerr")
  library("IlluminaHumanMethylation450kmanifest")
  library("IlluminaHumanMethylationEPICanno.ilm10b4.hg19")
  library("tictoc")
  library("mitch")
  library("kableExtra")
  library("beeswarm")
  library("missMethyl")
  library("vioplot")
})

>>>>

suppressPackageStartupMessages({
  library("limma")
  library("eulerr")
  library("IlluminaHumanMethylation450kmanifest")
  library("IlluminaHumanMethylationEPICanno.ilm10b4.hg19")
  library("tictoc")
  library("mitch")
  library("kableExtra")
  library("beeswarm")
  library("missMethyl")
})
